curatedMetagenomicData

### 2019-10-08 curatedMetagenomic_NS.Rmd
updated

#BiocManager::install("curatedMetagenomicData")
#BiocManager::install("ExperimentHub")
library(ExperimentHub)
library(curatedMetagenomicData)
suppressPackageStartupMessages(library(ExperimentHub))
library(phyloseq)
library(microbiome)
library(forcats)
library(stargazer)
library(ggpubr)

@@

any(taxa_sums(pseq.c) == 0)

>>>>

#BiocManager::install("curatedMetagenomicData")
#BiocManager::install("ExperimentHub")
library(ExperimentHub)
library(curatedMetagenomicData)
suppressPackageStartupMessages(library(ExperimentHub))
library(phyloseq)
library(microbiome)
library(forcats)
library(stargazer)
library(ggpubr)
library(tidyverse)

@@

any(taxa_sums(pseq.subset) == 0)
